|

### 2024-10-28 output/seminar-slideshow.qmd
Add manual plot of "Factor regression scores"

F1_COLOR <- PALETTE_BLUE["normal"]
F2_COLOR <- PALETTE_RASPBERRY["normal"]

item_colors   <- c(F1_COLOR |> rep(3), F2_COLOR |> rep(3))
factor_colors <- c('F1' = unname(F1_COLOR), 'F2' = unname(F2_COLOR))

@@

-   **Máxima Verosimilitud**

-   **Estimación Modal Bayesiana Empírica**

>>>>

F1_COLOR <- unname(PALETTE_BLUE["normal"])
F2_COLOR <- unname(PALETTE_RASPBERRY["normal"])

item_colors   <- c(F1_COLOR |> rep(3), F2_COLOR |> rep(3))
factor_colors <- c('F1' = F1_COLOR, 'F2' = F2_COLOR)

@@

::: {.fragment fragment-index="2"}
-   **Máxima Verosimilitud**

-   **Empirical Modal Bayes**
:::
::::

::: {.column .fragment fragment-index="1"}
```{r path-regression-scores}
# item_colors   <- c(F1_COLOR |> rep(3), F2_COLOR |> rep(3))
# factor_colors <- c('F1' = F1_COLOR, 'F2' = F2_COLOR)

# NOTE: Manual call to qgraph:
edge_list <- tribble(
  ~rhs, ~lhs,
  7,    1,
  7,    2,
  7,    3,
  8,    4,
  8,    5,
  8,    6,
  7,    8,
  8,    7
)
vSize <- c(10 |> rep(6), 14 |> rep(2))

qgraph::qgraph(
  edge_list,
  labels = c("I1", "I2", "I3", "I4", "I5", "I6", "F1", "F2") |>
    setNames(nm = _),
  label.cex = 1.6,
  shape = "square" |> rep(8),
  vsize = vSize, 
  vsize2 = vSize,
  color = "background" |> rep(8),
  border.color = c(F1_COLOR |> rep(3), F2_COLOR |> rep(3), F1_COLOR, F2_COLOR),
  border.width = 3,
  bidirectional = c(FALSE |> rep(6), TRUE, TRUE),
  directed = TRUE |> rep(8),
  curve = c(NA |> rep(6), 3, 3),
  edge.color = c(F1_COLOR |> rep(3), F2_COLOR |> rep(3), "black"),
  edge.width = 3,
  lty = 1,
  layout = matrix(
    c(
      -1, -0.6, -0.2, 0.2, 0.6, 1, -0.6, 0.6,
      -0.5 |> rep(6), 0.5 |> rep(2)
    ),
    ncol = 2
  ),
  mar = c(12, 1.3, 8, 1.3)
)
```
:::
::::::
